Parallel Multi-objective optimization using co-evolutionary islands and search space overlapping

### 2016-06-05 hpmoon-hpca.tex
Conseguí que funcionara la bibliografía
He descomentado un párrafo para probar, pero se puede borrar de nuevo si se quiere.

\begin{table}
\begin{center}
\begin{tabular}{|c|c|}
\hline
{\em Parameter Name} & {\em Value} \\ \hline
Number of islands ($P$) & 8, 32 and 128 \\ \hline
Chromosome size ($L$) & 512 and 2048 \\ \hline
Execution time (s) & 25 (for 512) and 100 (for 2048) \\ \hline \hline
Global population size ($N$) & 1024 \\ \hline
Selection type & Binary Tournament Selection \\ \hline
Replacement type & Generational \\ \hline 
Crossover type & SBX \\ \hline
Mutation  type & Polynomial\\ \hline
Mutation probability & 1/$L$ \\ \hline
Generations between migration & 5 \\ \hline
Individuals per migration & 1 \\ \hline
Selection for migration & Binary Tournament\\ \hline
Runs per configuration & 30 \\ \hline
\end{tabular}
\caption{Parameters and operators used in the experiments.}
\label{tab:parameters}
\end{center}
\end{table}

%The ECJ framework \cite{ECJ} has been used to run the experiments. Specific operators have been developed as new modules for ECJ, and they can be downloaded from our GitHub repository under a LGPL V3 License \footnote{\url{https://https://github.com/hpmoon/hpmoon-islands}}. The island model has been executed synchronously, using the ECJ Internal Island Model, in a CentOS 5.4 machine with Intel(R) Xeon(R) CPU E5520 @2.27GHz, 16 GB RAM, with Java Version 1.6.0\_16. As in this paper we only focus on the behaviour of our model in a single machine scenario (the islands share the same memory and processor), the migration time will not be as important factor as in a real distributed system. This task will be addressed in future works. %Pablo: no sé si decir esto aquí%
%
%

@@

\begin{acks}
Agradecimientos
\end{acks}

\bibliographystyle{splncs}
\bibliography{hpmoon-hpca}
%\begin{thebibliography}{99}
%\bibitem[Kopka and Daly(2003)]{R1}
%Kopka~H and Daly~PW (2003) \textit{A Guide to \LaTeX}, 4th~edn.
%Addison-Wesley.%

>>>>

\begin{table*}
\begin{center}
\begin{tabular}{|c|c|}
\hline
{\em Parameter Name} & {\em Value} \\ \hline
Number of islands ($P$) & 8, 32 and 128 \\ \hline
Chromosome size ($L$) & 512 and 2048 \\ \hline
Execution time (s) & 25 (for 512) and 100 (for 2048) \\ \hline \hline
Global population size ($N$) & 1024 \\ \hline
Selection type & Binary Tournament Selection \\ \hline
Replacement type & Generational \\ \hline 
Crossover type & SBX \\ \hline
Mutation  type & Polynomial\\ \hline
Mutation probability & 1/$L$ \\ \hline
Generations between migration & 5 \\ \hline
Individuals per migration & 1 \\ \hline
Selection for migration & Binary Tournament\\ \hline
Runs per configuration & 30 \\ \hline
\end{tabular}
\caption{Parameters and operators used in the experiments.}
\label{tab:parameters}
\end{center}
\end{table*}

The ECJ framework \cite{ECJ} has been used to run the
experiments. Specific operators have been developed as new modules for
ECJ, and they can be downloaded from our GitHub repository under a
LGPL V3 License
\footnote{\url{https://https://github.com/hpmoon/hpmoon-islands}}. The
island model has been executed synchronously, using the ECJ Internal
Island Model, in a CentOS 5.4 machine with Intel(R) Xeon(R) CPU E5520
@2.27GHz, 16 GB RAM, with Java Version 1.6.0\_16. As in this paper we
only focus on the behaviour of our model in a single machine scenario
(the islands share the same memory and processor), the migration time
will not be as important factor as in a real distributed system. This
task will be addressed in future works. %Pablo: no sé si decir esto
                                %aquí% 
%
%

@@

\begin{acks}
Acknowledgements
\end{acks}

\bibliographystyle{SageH}

\bibliography{hpmoon-hpca}
%\begin{thebibliography}{99}
%\bibitem[Kopka and Daly(2003)]{R1}
%Kopka~H and Daly~PW (2003) \textit{A Guide to \LaTeX}, 4th~edn.
%Addison-Wesley.%
